### 2022-02-22 sections/data_presel.tex
updates and change back the version to 0.5
update tables

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{Summary of preselection requirements. 
The leading and subleading $\had$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
\begin{center}
\begin{tabular}{c|ccc|c}
\toprule\toprule
\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & \multirow{2}{*}{hadronic channel} \\ 
& $t_h\lephad$ & $t_l\hadhad$ &  $t_l\had$ & $t_h\hadhad$\\
\midrule
Trigger & \multicolumn{3}{c|}{single-lepton trigger} & di-$\tau$ trigger  \\
Leptons  & \multicolumn{3}{c|}{=1 isolated $e$ or $\mu$}  & no isolated $e$ or $\mu$ \\
$\had$  & $=$1 $\had$ & $\geq$2 $\had$ & $=$1 $\had$ & $\geq$2 $\had$ \\
Electric charge ($Q$) & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} < 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} > 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ \\
Jets  &  3, $\geq$ 4 jets & $\geq$1 jets & 2, $\geq$3 jets & 3, $\geq$4 jets \\
$b$-tagging & \multicolumn{3}{c|}{=1 $b$-tagged jets} & =1 $b$-tagged jets\\
\bottomrule\bottomrule
\end{tabular}
\label{tab:preselection}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%
\begin{table*}[t!]
\caption{\small{Summary of preselection requirements. 
The leading and subleading $\had$ candidates are denoted by $\tau_{\mathrm{had,1}}$ and $\tau_{\mathrm{had,2}}$ respectively.}}
\begin{center}
\begin{tabular}{c|ccc|c}
\toprule\toprule
\multirow{2}{*}{Requirement} &  \multicolumn{3}{c|}{leptonic channel}  & \multicolumn{1}{c}{hadronic channel} \\ 
& $t_h\lephad$ & $t_l\hadhad$ &  $t_l\had$ & $t_h\hadhad$\\
\midrule
Trigger & \multicolumn{3}{c|}{single-lepton trigger} & di-$\tau$ trigger  \\
Leptons  & \multicolumn{3}{c|}{=1 isolated $e$ or $\mu$}  & =0 isolated $e$ or $\mu$ \\
$\had$  & $=$1 $\had$ & $\geq$2 $\had$ & $=$1 $\had$ & $\geq$2 $\had$ \\
Electric charge ($Q$) & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} < 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ & $Q_\ell \times Q_{\tau_{\mathrm{had,1}}} > 0$ & $Q_{\tau_{\mathrm{had,1}}} \times Q_{\tau_{\mathrm{had,2}}} < 0$ \\
Jets  &  3, $\geq$ 4 jets & $\geq$1 jets & 2, $\geq$3 jets & 3, $\geq$4 jets \\
$b$-tagging & \multicolumn{3}{c|}{=1 $b$-jets} & =1 $b$-jets\\
\bottomrule\bottomrule
\end{tabular}
\label{tab:preselection}
\end{center}
\end{table*}
%%%%%%%%%%%%%%%

### 2022-02-22 sections/introduction.tex
updates and change back the version to 0.5
update tables

\begin{table}[t!]
\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to Hc)$ and $\BR(t \to Hu)$.}}
\begin{center}
\tiny
\begin{tabular}{ccccc}
\toprule\toprule
& &\multirow{2}{*}{$\mathcal{L}$ [fb$^{-1}$]} & \multicolumn{1}{c}{95\% CL observed upper limits} & \multicolumn{1}{c}{95\% CL observed upper limits}  \\
& & 										    & \multicolumn{1}{c}{on $\BR(t \to Hc)$}            & \multicolumn{1}{c}{on $\BR(t \to Hu)$} \\
\midrule
\multirow{5}{*}{ATLAS}
& $H \to b\bar{b}$~\cite{fcnc36}                                          & 36.1         & $4.2 \times 10^{-3}$ & $5.2 \times 10^{-3}$ \\
& $H \to \gamma\gamma$~\cite{Aaboud:2017mfd}                              & 36.1         & $2.2 \times 10^{-3}$  & $2.4 \times 10^{-3}$  \\
& $H \to \tau\tau$ ($\lephad$, $\hadhad$)~\cite{fcnc36}                   & 36.1         & $1.9 \times 10^{-3}$  & $1.7 \times 10^{-3}$  \\ 
& $H \to WW^*, \tau\tau, ZZ^*$ ($2\ell$SS, $3\ell$)~\cite{Aaboud:2018pob} & 36.1         & $1.6 \times 10^{-3}$  & $1.9 \times 10^{-3}$\\ 
& Combination~\cite{fcnc36}                                               & 36.1         & $1.1 \times 10^{-3}$  & $1.2 \times 10^{-3}$  \\\midrule
\multirow{3}{*}{CMS} 
& $H \to b\bar{b}$~\cite{Sirunyan:2017uae}                                & 35.9         & $4.7 \times 10^{-3}$  & $4.7 \times 10^{-3}$  \\
& $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
& $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
%

\midrule
\bottomrule\bottomrule
\end{tabular}
\label{tab:limits_summary_ref}
\end{center}
\end{table}

>>>>

\begin{table}[t!]
\caption{\small{Summary of 95\% CL upper limits on $\BR(t \to Hc)$ and $\BR(t \to Hu)$ obtained from ATLAS and CMS Collaborations with Run 2 data.}}
\begin{center}
\small 
\begin{tabular}{ccccc}
\toprule\toprule
& &\multirow{2}{*}{$\mathcal{L}$ [fb$^{-1}$]} & \multicolumn{1}{c}{95\% CL observed upper limits} & \multicolumn{1}{c}{95\% CL observed upper limits}  \\
& & 										    & \multicolumn{1}{c}{on $\BR(t \to Hc)$}            & \multicolumn{1}{c}{on $\BR(t \to Hu)$} \\
\midrule
\multirow{5}{*}{ATLAS}
& $H \to b\bar{b}$~\cite{fcnc36}                                          & 36.1         & $4.2 \times 10^{-3}$ & $5.2 \times 10^{-3}$ \\
& $H \to \gamma\gamma$~\cite{Aaboud:2017mfd}                              & 36.1         & $2.2 \times 10^{-3}$  & $2.4 \times 10^{-3}$  \\
& $H \to \tau\tau$ ($\lephad$, $\hadhad$)~\cite{fcnc36}                   & 36.1         & $1.9 \times 10^{-3}$  & $1.7 \times 10^{-3}$  \\ 
& $H \to WW^*, \tau\tau, ZZ^*$ ($2\ell$SS, $3\ell$)~\cite{Aaboud:2018pob} & 36.1         & $1.6 \times 10^{-3}$  & $1.9 \times 10^{-3}$\\ 
& Combination~\cite{fcnc36}                                               & 36.1         & $1.1 \times 10^{-3}$  & $1.2 \times 10^{-3}$  \\\midrule
\multirow{3}{*}{CMS} 
& $H \to b\bar{b}$~\cite{Sirunyan:2017uae}                                & 35.9         & $4.7 \times 10^{-3}$  & $4.7 \times 10^{-3}$  \\
& $H \to b\bar{b}$~\cite{CMS:2021gfa}                                     & 137          & $9.4 \times 10^{-4}$  & $7.9 \times 10^{-4}$  \\
%& $H \to \gamma\gamma$~\cite{CMS-PAS-TOP-20-007}                          & 137          & $7.3 \times 10^{-4}$  & $1.9 \times 10^{-4}$  \\
% 
\bottomrule\bottomrule
\end{tabular}
\label{tab:limits_summary_ref}
\end{center}
\end{table}

### 2022-02-22 sections/simulated_samples.tex
updates and change back the version to 0.5
update tables

\begin{table}
\footnotesize
\centering
\caption{Overview of the MC generators used for the main signal and background samples}
\begin{tabular}[h]{l|c|c|c|c|c|c}
\hline \hline
\multirow{2}{*}{Process} & \multicolumn{2}{c|}{Generator} & \multicolumn{2}{c|}{PDF set} & \multirow{2}{*}{Tune} & \multirow{2}{*}{Order} \\ \cline{2-5}
        &  ME   &  PS    &  ME  & PS &   &  \\\hline
$tt(qH)$ Signal & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$tH$ Signal & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$W/Z$+jets & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline
\ttbar & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
Single top & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$t\bar{t}X$ & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
Diboson & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline\hline
\end{tabular}
\label{mob}
\end{table}

>>>>

%  \begin{table}
%  \footnotesize
%  \centering
%  \caption{Overview of the MC generators used for the main signal and background samples.}
%  \begin{tabular}[h]{l|c|c|c|c|c|c}
%  \hline \hline
%  \multirow{2}{*}{Process} & \multicolumn{2}{c|}{Generator} & \multicolumn{2}{c|}{PDF set} & \multirow{2}{*}{Tune} & \multirow{2}{*}{Order} \\ \cline{2-5}
%          &  ME   &  PS    &   ME  & PS &   &  \\\hline
%  $tt(qH)$ Signal & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
%  $tH$ Signal & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
%  $W/Z$+jets & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline
%  \ttbar & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
%  Single top & Powheg & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
%  $t\bar{t}X$ & MadGraph5\_aMC@NLO & Pythia8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
%  Diboson & \multicolumn{2}{c|}{Sherpa 2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & Sherpa & NLO/LO \\ \hline\hline
%  \end{tabular}
%  \label{mob}
%  \end{table}

\begin{table}
\footnotesize
\centering
\caption{Overview of the MC generators used for the main signal and background samples.}
\begin{tabular}[h]{l|c|c|c|c|c|c}
\hline \hline
\multirow{2}{*}{Process} & \multicolumn{2}{c|}{Generator} & \multicolumn{2}{c|}{PDF set} & \multirow{2}{*}{Tune} & \multirow{2}{*}{Order} \\ \cline{2-5}
        &  ME   &  PS    &   ME  & PS &   &  \\\hline
$tt(qH)$ Signal & \powheg & \pythia~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$tH$ Signal & \amcatnlolong & \pythia~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$W/Z$+jets & \multicolumn{2}{c|}{\sherpa~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & \sherpa & NLO/LO \\ \hline
\ttbar & \powheg & \pythia~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
Single top & \powheg & \pythia~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
$t\bar{t}X$ & \amcatnlolong & \pythia~8 & NNPDF30NLO & NNPDF23LO & A14 & NLO \\ \hline
Diboson & \multicolumn{2}{c|}{\sherpa~2.2.1} & \multicolumn{2}{c|}{NNPDF30NNLO} & \sherpa & NLO/LO \\ \hline\hline
\end{tabular}
\label{mob}
\end{table}

### 2022-02-22 sections/strategy_Htautau.tex
updates and change back the version to 0.5
update tables

\begin{table}
\centering
\caption{Overview of the signal regions and the control regions used for fake tau scale factor derivation in leptonic channels.}
\label{tab:srcr}
\begin{tabular}[h]{c|c|c|c|c|c|c}
\hline \hline
\multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
\multirow{7}{*}{SR}&$t_l\thadhad$     & 1     & any                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
&$t_l\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
&$t_l\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
&$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
&$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
&$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
&$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
\multirow{6}{*}{CRtt}&$t_lt_l1b\tauhad$ & 1     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
&$t_lt_l2b\tauhad$      & 2     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
&$t_lt_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
&$t_lt_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ OS\\ \cline{2-7}
&$t_lt_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
&$t_lt_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_l\tauhad$ OS\\ \hline
\end{tabular}
\end{table}

>>>>

%   \begin{table}
%   \centering
%   \caption{Overview of the signal regions and the control regions used for fake tau scale factor derivation in leptonic channels.}
%   \label{tab:srcr}
%   \begin{tabular}[h]{c|c|c|c|c|c|c}
%   \hline \hline
%   \multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
%   \multirow{7}{*}{SR}&$t_l\thadhad$     & 1     & any                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
%   &$t_l\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
%   &$t_l\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
%   &$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
%   &$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
%   &$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
%   &$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
%   \multirow{6}{*}{CRtt}&$t_lt_l1b\tauhad$ & 1     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
%   &$t_lt_l2b\tauhad$      & 2     & any                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
%   &$t_lt_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
%   &$t_lt_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ OS\\ \cline{2-7}
%   &$t_lt_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
%   &$t_lt_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_l\tauhad$ OS\\ \hline
%   \end{tabular}
%   \end{table}

\begin{table}
\centering
\caption{Overview of the signal regions and the control regions used for fake tau scale factor derivation in leptonic channels.}
\label{tab:srcr}
\begin{tabular}[h]{c|c|c|c|c|c|c}
\hline \hline
\multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
\multirow{7}{*}{SR}&$t_l\thadhad$     & 1     & $\ge0$                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
&$t_l\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
&$t_l\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_l\tauhad$ SS\\ \cline{2-7}
&$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
&$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
&$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
&$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
\multirow{6}{*}{CRtt}&$t_lt_l1b\tauhad$ & 1     & $\ge0$                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
&$t_lt_l2b\tauhad$      & 2     & $\ge0$                           & 2      & 1                     & $t_lt_l$ OS\\ \cline{2-7}
&$t_lt_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
&$t_lt_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_l\tauhad$ OS\\ \cline{2-7}
&$t_lt_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_l\tauhad$ SS\\ \cline{2-7}
&$t_lt_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_l\tauhad$ OS\\ \hline
\end{tabular}
\end{table}

### 2022-02-22 sections/systematic_uncertainties.tex
updates and change back the version to 0.5
update tables

\begin{table}[h!]
\caption{List of relative uncertainties of the signal strength from the combined fit. The uncertainties are symmetrised for presentation and grouped into the categories described in the text.}
\label{tab:had_sys_impact}
\begin{center}
\begin{tabular}{%
@{}l%
S%
S%
@{}%
}
\toprule
\multirow{2}{*}{Source of uncertainty}      & \multicolumn{2}{c}{$\Delta\mu/\mu [\%]$} \\
                                            & \multicolumn{1}{c}{$t\rightarrow uH$} & \multicolumn{1}{c}{$t\rightarrow cH$} \\\midrule
Lepton                                  & 0.6           &1.0         \\
Met                                     & 0.7           &0.8         \\
Luminosity and Pileup                   & 1.0           &1.3         \\
Theoretical uncertainty in other MC     & 2.1           &2.9         \\
Jets                                    & 2.4           &3.2         \\
Flavour tagging                         & 2.7           &3.7         \\
Misidentified $\tau$                    & 3.4           &4.8         \\
Theoretical uncertainty in $t\bar{t}$   & 2.9           &4.3         \\
Hadronic $\tau$ decays                  & 3.3           &4.4         \\
Theoretical uncertainty in signal       & 5.3           &7.0         \\\midrule
Total statistics uncertainty            & 5.1           &7.0         \\
Total systematic uncertainty            & 11.2          &15.4        \\ \midrule
Total                                   & 12.3          &16.9        \\
\bottomrule
\end{tabular} 
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\caption{List of relative uncertainties of the signal strength from the combined fit. The uncertainties are symmetrised for presentation and grouped into the categories described in the text.}
\label{tab:had_sys_impact}
\begin{center}
\begin{tabular}{%
@{}l%
S%
S%
@{}%
}
\toprule\toprule
\multirow{2}{*}{Source of uncertainty}      & \multicolumn{2}{c}{$\Delta\mu/\mu [\%]$} \\
                                            & \multicolumn{1}{c}{$t\rightarrow uH$} & \multicolumn{1}{c}{$t\rightarrow cH$} \\\midrule
%Lepton                                  & 0.6           &1.0         \\
%Met                                     & 0.7           &0.8         \\
%Luminosity and Pileup                   & 1.0           &1.3         \\
%Theoretical uncertainty in other MC     & 2.1           &2.9         \\
%Jets                                    & 2.4           &3.2         \\
%Flavour tagging                         & 2.7           &3.7         \\
%Misidentified $\tau$                    & 3.4           &4.8         \\
%Theoretical uncertainty in $t\bar{t}$   & 2.9           &4.3         \\
%Hadronic $\tau$ decays                  & 3.3           &4.4         \\
%Theoretical uncertainty in signal       & 5.3           &7.0         \\\midrule
%Total statistics uncertainty            & 5.1           &7.0         \\
%Total systematic uncertainty            & 11.2          &15.4        \\ \midrule
%Total                                   & 12.3          &16.9        \\

Lepton ID                               & 0.6           &1.0         \\
Met                                     & 0.7           &0.8         \\
Fake lepton  modeling                   & 0.9           &1.1         \\
Luminosity and Pileup                   & 0.9           &1.3         \\
Other MC modeling                       & 2.1           &2.9         \\
JES and JER                             & 2.4           &3.2         \\
Flavour tagging                         & 2.7           &3.7         \\
$t\bar{t}$ modeling                     & 2.9           &4.3         \\
Fake $\tau$ modeling                    & 3.2           &4.6         \\
$\tau$ ID                               & 3.3           &4.4         \\
Signal modeling including Br($H\to\tau\tau$)       & 5.3           &7.0         \\\midrule
Total systematic uncertainty            & 11.2          &15.5        \\ 
Total statistics uncertainty            & 5.1           &7.0         \\\midrule
Total                                   & 12.3          &17.0        \\

%tuH:
%Fake LEP method    0.00919939  ( +0.00919939, -0.00919939 )
%Fake method    0.0323159  ( +0.0323159, -0.0323159 )
%FullSyst    0.112111  ( +0.112111, -0.112111 )
%Gammas    0.0509968  ( +0.0509968, -0.0509968 )
%Instrument    0.0093934  ( +0.0093934, -0.0093934 )
%JET    0.0235705  ( +0.0235705, -0.0235705 )
%Lepton    0.00568277  ( +0.00568277, -0.00568277 )
%MET    0.00704844  ( +0.00704844, -0.00704844 )
%SignalTheory    0.0526104  ( +0.0526104, -0.0526104 )
%TAU    0.032714  ( +0.032714, -0.032714 )
%Theory    0.0210686  ( +0.0210686, -0.0210686 )
%btag    0.027376  ( +0.027376, -0.027376 )
%ttbarTheory    0.0289194  ( +0.0289194, -0.0289194 )

%tcH:
%Fake LEP method    0.010914  ( +0.010914, -0.010914 )
%Fake method    0.0455017  ( +0.0455017, -0.0455017 )
%FullSyst    0.154686  ( +0.154686, -0.154686 )
%Gammas    0.0700708  ( +0.0700708, -0.0700708 )
%Instrument    0.0131647  ( +0.0131647, -0.0131647 )
%JET    0.0320897  ( +0.0320897, -0.0320897 )
%Lepton    0.0104552  ( +0.0104552, -0.0104552 )
%MET    0.00841447  ( +0.00841447, -0.00841447 )
%SignalTheory    0.0699833  ( +0.0699833, -0.0699833 )
%TAU    0.0437292  ( +0.0437292, -0.0437292 )
%Theory    0.029182  ( +0.029182, -0.029182 )
%btag    0.0367613  ( +0.0367613, -0.0367613 )
%ttbarTheory    0.0427391  ( +0.0427391, -0.0427391 )

\bottomrule\bottomrule
\end{tabular} 
\end{center}
\end{table}
